PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-28 paper/paper.tex
added boundary detection section

@@

>>>>

\def\eg{\emph{e.g.\/}}
\def\ie{\emph{i.e.\/}}
\def\etc{\emph{etc.\/}}
\def\etal{\emph{et al.\/}}
\DeclareMathOperator*{\median}{median}

@@

\subsection{Segmentation}

Evaluation criteria for segmentation fall into two categories: boundary annotation, and structural annotation.
\emph{Boundary annotation} is the task of predicting the times at which structural changes occur, such as when a \emph{verse} transitions to a \emph{refrain}.
\emph{Structural annotation} is the task of assigning labels to detected segments.  
The estimated labels may be arbitrary strings --- such as $A$, $B$, $C$, \etc{} --- and they need not describe functional concepts.

In both tasks, we assume that annotations take the form of a partitioning of the track 
into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
Structural annotation additionally requires that each interval be assigned a label $y_i$.

\subsubsection{Boundary annotation}

Within boundary annotation, there are two categories of evaluation metrics: detection,
and deviation~\cite{turnbull2007supervised}.

\emph{Boundary detection} measures the precision, recall, and f-measure of boundary prediction within a tolerance window.
Let $B_R$ ($B_E$) denote the set of unique interval boundaries in the reference (estimated) annotation, and let $W$ denote 
a tolerance window, typically either $0.5$s or $3.0$s.  
A \emph{hit} is defined as a pair $b_e \in B_E$, $b_r \in B_R$ such that $|b_e - b_r|
\leq W$.

To define detection metrics, we require that no estimated boundary is counted for more than one reference boundary, and vice versa.
This is accomplished by computing a maximum bipartite matching $H_W$ between $B_E$ and $B_R$ (subject to the window constraint $W$) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.  
Precision and recall with window $W$ are defined as
\begin{align}
P_W(B_R, B_E) &:= \frac{|H_W|}{|B_E|}\\
R_W(B_R, B_E) &:= \frac{|H_W|}{|B_R|},
\end{align}
and the corresponding f-measure is defined by taking their harmonic mean.

\emph{Boundary deviation} is comprised of two scores, which measure the median time between a reference boundary and its nearest corresponding estimated boundary, and vice versa.
These two metrics have previously been defined as \emph{true-to-predicted} (T-to-P) and \emph{predicted-to-true} (P-to-T), though in the terminology of this document, we use 
alternative naming of \emph{reference-to-estimated} (R-to-E) and \emph{estimated-to-reference} (E-to-R):
\begin{align}
\text{R-to-E}(B_R, B_E) &:= \displaystyle\median_{b_r \in B_R} \min_{b_e \in B_E} \left|b_r - b_e\right|\\
\text{E-to-R}(B_R, B_E) &:= \displaystyle\median_{b_e \in B_E} \min_{b_r \in B_R} \left|b_r - b_e\right|.
\end{align}

\subsubsection{Structural annotation}
